---
title: "Non-informative censoring computations"
author: "Despina Konstantinidou"
date: "17/06/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#packages
library(tidyverse)
library(survival)
library(asaur)
library(modelr)
library(broom)
library(haven)
library(flexsurv)

```


## Data

```{r, warning=FALSE, echo=FALSE,message=FALSE}
data <- read.table("liverdata.dat",fileEncoding = "UTF-8",header=TRUE,na=".")

# simple correction for observed zero times
data$survtime<-ifelse(data$survtime==0,data$survtime+0.5,data$survtime)
data <- data.frame(data)

```

The general principle is that both packages `survival` and `flexsurv` assume non-informative censoring by default and we only define the custom distrubutions that we want to use. For each custom distribution we check if it gives the same results as the pre-loaded distributions in flexusurv, except for a sign changed in the location paramters.


## Weibull

```{r w, warning=FALSE, echo=FALSE,message=FALSE}

#custom Weibull
Hweib<-function(x,theta1,theta2){
  (theta1*x)^theta2
}

hweib<-function(x,theta1,theta2){
 theta2*theta1^theta2*x^{theta2-1}
}

custom.weib <- list(name = "weib",  
                      pars = c("theta1", "theta2"),
                      location = "theta1", 
                      transforms = c(log, log),
                      inv.transforms = c(exp, exp), 
                      inits = function(t) c(exp(-median(log(t))), 1/mad(log(t),constant=1)))


# null model
fit_weib_no_cov <- flexsurvreg(Surv(survtime,status) ~ 1, 
                      data = data,
                      dist = custom.weib)

# covariate model
fit_weib_cov <- flexsurvreg(Surv(survtime,status) ~ UKELD+recip_age, 
                      data = data,
                      dist = custom.weib)
```

```{r}
# pre-loaded Weibull

# null model
fit_weib_no_cov1 <- flexsurvreg(Surv(survtime,status) ~ 1, 
                      data = data,
                      dist = 'weibull')

# covariate model
fit_weib_cov1 <- flexsurvreg(Surv(survtime,status) ~ UKELD + recip_age, 
                      data = data,
                      dist = 'weibull')
```



## Gompertz


```{r g, warning=FALSE, echo=FALSE,message=FALSE}

#custom Gompertz
Hgompt<-function(x,theta1,theta2){
  exp((theta1*x)^theta2)-1
}
hgompt<-function(x,theta1,theta2){
 theta1*theta2*((theta1*x)^{theta2-1})*exp((theta1*x)^theta2)
}

custom.gompt <- list(name = "gompt",  
                      pars = c("theta1", "theta2"),
                      location = "theta1", 
                      transforms = c(log, log),
                      inv.transforms = c(exp, exp), 
                      inits = function(t) c(0.001,1))



# null model
fit_gompt_no_cov <- flexsurvreg(Surv(survtime,status) ~ 1, 
                      data = data,
                      dist = custom.gompt)

# covariate model
fit_gompt_cov <- flexsurvreg(Surv(survtime,status) ~ UKELD + recip_age, 
                      data = data,
                      dist = custom.gompt)

```

```{r}
# pre-loaded Gompertz
fit_gompt_no_cov1 <- flexsurvreg(Surv(survtime,status) ~ 1, 
                      data = data,
                      dist = 'gompertz')

# covariate model
fit_gompt_cov1 <- flexsurvreg(Surv(survtime,status) ~ UKELD+recip_age, 
                      data = data,
                      dist = 'gompertz')

```



## Log-logistic

```{r,warning=FALSE, echo=FALSE,message=FALSE}

#custom Log-logistic
Hllog<-function(x,theta1,theta2){
  log(1+(theta1*x)^theta2)
}
hllog<-function(x,theta1,theta2){
 (theta2*theta1^{theta2}*x^{theta2-1})/(1+(theta1*x)^theta2)
}

custom.llog <- list(name = "llog",  
                  pars = c("theta1", "theta2"),
                  location = "theta1", 
                  transforms = c(log, log),
                  inv.transforms = c(exp, exp), 
                  inits = function(t) c(exp(-median(log(t))), 
                                        1/mad(log(t),constant=1)))

# null model
fit_ll_no_cov <- flexsurvreg(Surv(survtime,status) ~ 1, 
                      data = data,
                      dist = custom.llog)

# covariate model
fit_ll_cov <- flexsurvreg(Surv(survtime,status) ~ UKELD + recip_age, 
                      data = data,
                      dist = custom.llog)


```

```{r}
#pre-loaded Log-logistic

# null model
fit_ll_no_cov1 <- flexsurvreg(Surv(survtime,status) ~ 1, 
                      data = data,
                      dist = 'llogis')

# covariate model
fit_ll_cov1 <- flexsurvreg(Surv(survtime,status) ~ UKELD+recip_age, 
                      data = data,
                      dist = 'llogis')
```




